
\part[index]{Introduction}

\BlockClassSingle{manual-title-block}{%
\BlockClassSingle{manual-title}{Manual for Package \PGFPlots{}}
\BlockClassSingle{manual-version}{2D/3D Plots in \LaTeX{}, Version \pgfplotsversion\ -- \the\year{}}
\BlockClassSingle{manual-html-title}{Unofficial HTML Version}
\BlockClassSingle{manual-html-explanation}{%
This HTML version of the documentation is maintained by Dominik Peters, 
and is produced using the \href{https://ctan.org/pkg/lwarp?lang=en}{\texttt{lwarp}} package.}
\BlockClassSingle{manual-authorship-explanation}{%
Author of the \PGFPlots{} manual: Dr. Christian Feuersänger.}
\BlockClassSingle{manual-authorship-explanation}{%
\href{http://sourceforge.net/projects/pgfplots}{http://sourceforge.net/projects/pgfplots}}
}

\BlockClassSingle{abstract-block}{%
\BlockClassSingle{abstract-heading}{Abstract}
\PGFPlots{} draws high-quality function plots in normal or logarithmic
        scaling with a user-friendly interface directly in \TeX{}. The user
        supplies axis labels, legend entries and the plot coordinates for one or
        more plots and \PGFPlots{} applies axis scaling, computes any logarithms
        and axis ticks and draws the plots. It supports line plots, scatter
        plots, piecewise constant plots, bar plots, area plots, mesh and surface
        plots, patch plots, contour plots, quiver plots, histogram plots, box
        plots, polar axes, ternary diagrams, smith charts and some more. It is
        based on Till Tantau's package \PGF{}/\Tikz{}.%
}

This package provides tools to generate plots and labeled axes easily. It draws
normal plots, log plots and semi-log plots, in two and three dimensions. Axis
ticks, labels, legends (in case of multiple plots) can be added with key--value
options. It supports line plots, scatter plots, piecewise constant plots, bar
plots, area plots, mesh and surface plots, patch plots, contour plots, quiver
plots, histogram plots, box plots, polar axes, ternary diagrams, smith charts
and some more. It can cycle through a set of predefined line/marker/color
specifications.

In summary, its purpose is to simplify the generation of high-quality function
and/or data plots, and solving the problems of
%
\begin{itemize}
    \item consistency of document and font type and font size,
    \item direct use of \TeX{} math mode in axis descriptions,
    \item consistency of data and figures (no third party tool necessary),
    \item inter-document consistency using preamble configurations and
        styles.
\end{itemize}
%
Although not necessary, separate |.pdf| or |.eps| graphics can be generated
using the |external| library developed as part of \Tikz{}.

You are invited to use \PGFPlots{} for visualization of medium sized data sets
in two and three dimensions.

It is based on Till Tantau's package \PGF{}/\Tikz{}.
